Toward a More Accessible and Reproducible ISLS Conference Proceedings Paper: A Practical Workshop Using Cutting-Edge Tools

### 2021-01-09 paper_contents.tex

\subsection{Intended Audience}
We believe this tutorial would be helpful for all ISLS participants who plan to submit papers to future ISLS. The use of the LaTeX and Overleaf templates would be especially helpful for those who want to improve the quality of the formatting for their ISLS submission, feel the existing Word template is difficult to work with, or would like a better tool for collaborative writing. The use of the RMarkdown would benefit those who wish to integrate their data analysis into their writing to improve the reproducibility and transparency of their work, and those who would like to make that work available in more accessibility friendly formats.

>>>>

\subsection{Intended Audience}
We believe this tutorial would be helpful for all ISLS participants who plan to submit papers to future ISLS. The use of the LaTeX and Overleaf templates would be especially helpful for those who want to improve the quality of the formatting for their ISLS submission, feel the existing Word template is difficult to work with, or would like a better tool for collaborative writing. The use of the RMarkdown would benefit those who wish to integrate their data analysis into their writing to improve the reproducibility and transparency of their work, and those who would like to make that work available in more accessibility-friendly formats.
